Happiness versus Income Awareness

### 2022-02-28 outputs/paper/Paper2-copy.Rmd
final

\newpage
# Introduction

@@

Income Rank —- denotes the respondent's position in the distribution of household income for the current year. Respondents were questioned about their yearly gross household income using bins, as is customary in household surveys.

Perceived Rank -- Based on the question: "Would you say that your economic condition is... in contrast to other Norwegians?" Slightly worse than average; Average; Slightly better than average; Much better than average.

@@

When looking for tax documents on the internet, it's necessary to be familiar with the most often used words, as seen in Figure 1. By inserting the word "YouTube," we've provided a jumping-off point for other users. Norway has been located, which signifies that the quest has come to an end. A skattelister's test in Norway is no longer solely dependent on weather predictions as of the year 2010. A skattelister search accounted for almost one out of every five YouTube searches. This indicates that there is a great deal of interest in the tax listings. Norwegians were found to be more prone than the overall population to look for tax paperwork, according to the study. While it is true that people have an increased interest in taxation, tax lists were searched approximately three times more often than actual taxes.
```{r echo=FALSE}
#Since the original data contain many observations that exceed the maximum load and are useless for further analysis, we create a new table with the corresponding variables and then plot a bar graph.
country_hah <- read.table(text = "keyword    Norway    Sweden
                  'Skattelister'   21.686750      0
                  'Tax'  7.228915      2.325581
                  'Weather'   18.072290      23.255819
                  'Youtube'   100.000000      100.000000
                  ",
                  header = TRUE, stringsAsFactors = FALSE)

@@

## Limitations
There existed very limited used of the online tax lists for the purpose of learning salary. The actual percentage turned out to be only 26 percent of the individuals and may be only for the purpose of snooping not researching. Plus, the nature of the data was described as "completely useless" for salary comparisons practices[@citenrk]. On top of that, the Norwegian tax records reveal comprehensive income including gains outside of the payroll which puts additional uncertainties comparing to the benchmark of the website of state employees studied in [@citecard].

## Ethics

## Future

@@

>>>>

Code and data are available at ^[ https://github.com/XiaoBai-blip/STA304-Paper-2]

DOI of my replication is available at ^[https://doi.org/10.48152/ssrp-2dzq-6x71]

\newpage

# Introduction

@@

Income Rank: Denotes the respondent's position in the distribution of household income for the current year. Respondents were questioned about their yearly gross household income using bins, as is customary in household surveys.

Perceived Rank: Based on the question: "Would you say that your economic condition is... in contrast to other Norwegians?" Slightly worse than average; Average; Slightly better than average; Much better than average.

@@

\newpage
## Results

When looking for tax documents on the internet, it's necessary to be familiar with the most often used words, as seen in Figure 1. By inserting the word "YouTube," we've provided a jumping-off point for other users. Norway has been located, which signifies that the quest has come to an end. A skattelister's test in Norway is no longer solely dependent on weather predictions as of the year 2010. A skattelister search accounted for almost one out of every five YouTube searches. This indicates that there is a great deal of interest in the tax listings. Norwegians were found to be more prone than the overall population to look for tax paperwork, according to the study. While it is true that people have an increased interest in taxation, tax lists were searched approximately three times more often than actual taxes.

```{r echo=FALSE}
#Since the original data contain many observations that exceed the maximum load and are useless for further analysis, we create a new table with the corresponding variables and then plot a bar graph.
country_hah <- read.table(text = "keyword    Norway    Sweden
                  'Skattelister'   21.686750      0
                  'Tax'  7.228915      2.325581
                  'Weather'   18.072290      23.255819
                  'Youtube'   100.000000      100.000000
                  ",
                  header = TRUE, stringsAsFactors = FALSE)

@@

This paper is reproduction of "The Effects of Income Transparency on Well-Being: Evidence from a Natural Experiment," written by Ricardo Perez-Truglia, is included in this publication [@citehappy]. Because this is a replication research, the model used in this publication is not the same as the model used in the original work. There existed very limited used of the online tax lists for the purpose of learning salary. The actual percentage turned out to be only 26 percent of the individuals and may be only for the purpose of snooping not researching. Plus, the nature of the data was described as "completely useless" for salary comparisons practices [@citenrk]. On top of that, the Norwegian tax records reveal comprehensive income including gains outside of the payroll which puts additional uncertainties comparing to the benchmark of the website of state employees studied in [@citecard].

## Limitations and Future
Due to our limited expertise of the subject matter, we chose two components of the paper for replication. We started with the first linear regression model and repeated it without using a control variable to see how it performed. The findings revealed an association between income transparency and well-being in the same manner that was indicated in the original study; however, the number we replicated was not precisely the same as the original paper. As a consequence of the minimal replication information supplied by the publication and the knowledge base, we have been successful in reproducing a bare-bone regression model utilizing the same OLS regression and obtaining the same outcome as before. I made several recommendations based on the constraints I saw. First and foremost, if at all feasible, the replication process should begin with data collection. Furthermore, certain fundamental demographic factors should be gathered and documented in the data so that I may include them into the model to account for any tiny variances across groups and therefore increase the accuracy of forecasts.

## Ethics
On the 10 Simple Rules for Responsible Big Data Research, we will rely on the advice provided by @citeTen. The ten rules are as follows (according to @citeTen ). We acknowledge that 1) The data is based on survey and people, and these data can be harmful. 2) The data is privacy. 3) The share of the data package is ethical. 4) The study has limitations.

@@

\newpage
